Supplementary material for "Hack Weeks as a model for Data Science Education and Collaboration"

### 2017-12-19 sections/intro.tex

As of the publication of this paper, we have run eight such hack week events: four focused on Astronomy, two focused on Neuroscience, and two focused on Geoscience.
Below we will share some of the philosophy behind the hack week model, practical lessons we have learned in organizing these events, and recommendations for future hack weeks in other disciplines.

>>>>

As of the publication of this paper, we have run eight such hack week events: four focused on Astronomy, two focused on Neuroscience, and two focused on Geoscience.
Below we will share some of the philosophy behind the hack week model, results from surveys of participants, and practical lessons we have learned in organizing these events, as well as recommendations for future hack weeks in other disciplines (supplementary materials provide additional details on the practical aspects of organizing these events).

### 2017-12-19 sections/participants.tex

No matter the selection procedures used, we encourage organizers to critically examine their cohort selection, experiment with new approaches, and routinely evaluate the different steps in their procedure.  For example, merit scores can be interrogated for shared biases, and one can plot the demographics both before and after the initial selection step to diagnose whether certain groups are preferentially selected or excluded.

>>>>

No matter the selection procedures used, we encourage organizers to critically examine their cohort selection, experiment with new approaches, and routinely evaluate the different steps in their procedure.  For example, merit scores can be interrogated for shared biases, and one can plot the demographics both before and after the initial selection step to diagnose whether certain groups are preferentially selected or excluded (see also the Supplementary materials for more details on how the previous hack weeks approached this problem).

### 2017-12-19 sections/why.tex

It is worth noting that the reasons for participants to attend a hack week are as diverse as the reasons for running such an event. 
Beginner participants may attend primarily to learn a new technique and may not have an explicit plan for project based work, while others may attend to gain experience in mentoring, or to focusing on an existing project already in progress.

>>>>

It is worth noting that the reasons for participants to attend a hack week are as diverse as the reasons for running such an event.
Beginner participants may attend primarily to learn a new technique and may not have an explicit plan for project based work, while others may attend to gain experience in mentoring, or to focusing on an existing project already in progress (for more details on setting objectives for a hack week, see supplementary materials)
